\setcounter{page}{1}
\chapter*{Acknowledgment}
\addcontentsline{toc}{chapter}{Acknowledgment}

I would like to express my sincere gratitude and appreciation
to my academic supervisor, \textbf{Mrs. Asma Kerkeni}, for her invaluable guidance,
insightful advice, and unwavering support throughout this internship journey.
Her expertise, enthusiasm, and dedication have been a constant source
of inspiration and motivation.

I would also like to extend my deepest thanks to my technical supervisor,
\textbf{Fahmi Boumaiza}, for his technical mentorship, and guidance throughout
the project. His knowledge and expertise in software development were
of great help in shaping this project and ensuring its success,
and I have learned a lot from him.

I am grateful to both my supervisors for providing me with the opportunity
to work on this challenging and exciting project, which has enriched
my knowledge and skills in software development. Their support and mentorship
have been crucial to my academic and professional growth.

Furthermore, I would like to acknowledge the esteemed members of the committee,
\textbf{Mrs. Aida Lahouij} as the president of the committee, and \textbf{Mrs. Manel Sekma}
as the examiner of this report. Their valuable insights and expertise significantly contribute
to the assessment and refinement of this project's outcomes. I deeply appreciate their
willingness to invest their time and knowledge in this evaluation process.

Finally, I would like to thank the entire team at \textbf{Satoripop}
for their cooperation, encouragement, and support throughout this journey.
Their insightful feedback and suggestions made my work enjoyable and productive.