\chapter*{Introduction}
\addcontentsline{toc}{chapter}{Introduction}

In today's rapidly evolving digital landscape, the insurance, banking, and finance sectors 
are facing unprecedented challenges and opportunities. As customers increasingly expect seamless
and personalized experiences, it has become imperative for companies in these industries to undergo 
a digital transformation. This shift not only enhances customer engagement and satisfaction but also 
boosts operational efficiency and employee productivity. 

Recognizing this need, the "Convergence" project was initiated to provide innovative solutions 
that facilitate the digital transformation process, enabling organizations to stay competitive, 
deliver exceptional customer experiences, and achieve sustainable growth in the ever-changing 
marketplace.

Within the "Convergence" ecosystem, various tools and sub-projects are assembled, each playing 
a crucial role in this shared mission. Among these modules, we will be focusing on the Notification
Center, as it plays a pivotal role in enhancing communication by providing a centralized system 
for timely and relevant notifications.

This report is structured in several chapters to provide a comprehensive overview of the project's 
progression. It begins with an introduction to the project context, including a profile of the 
host organization and an overview of the project itself. The challenges and problems faced in the 
insurance and finance sectors are also assessed.

The second chapter discusses the initial sprint of the project, which revolves around gathering 
requirements, defining specifications and setting the groundwork to start the project execution.

Subsequent chapters delve into the specific releases of the project, outlining the specification, 
design and implementation steps. Each chapter provides a summary of the key findings and progress 
made during the respective phase.